---
title: "EPIONCHO-IBM"
author:
- name: Jonathan Hamley
  affiliation: Imperial College London, University of Bern
- name: Martin Walker
  affiliation: Royal Veterinary College, Imperial College London
- name: Philip Milton
  affiliation: Imperial College London
date: "May 15, 2021"
output:
  html_document:
    df_print: paged
  word_document: default
  radix::radix_article: default
  pdf_document: default
description: |
  A stochastic, individual-based model for onchocerciasis transmission
---

**EPIONCH0-IBM is a stochastic, individual-based model for onchocerciasis transmission. A mathematical description can be found at https://doi.org/10.1371/journal.pntd.0007557.**

# 1. System requirements

EPIONCHO IBM is written in R (1) which is freely available for installation on Windows, Mac OS and Linux platforms from https://www.r-project.org. It is also recommended to install R Studio https://www.rstudio.com which provides a helpful user interface for R. EPIONCHO-IBM has been tested on Mac OS and Windows, but should be compatible with Linux and run on any desktop or laptop machine.

# 2. Installation guide

The model code can be downloaded and installed directly from a GitHub repository (https://github.com/jonathanhamley/EPIONCHO-IBM). The RCurl (2) package must be installed to do this. Installation should take no more than a few seconds on most desktop or laptop machines.


```{r, eval=F, echo = TRUE, collapse=TRUE}
install.packages("RCurl")
script <- RCurl::getURL("https://raw.githubusercontent.com/jonathanhamley/EPIONCHO-IBM/master/EPIONCHO_IBM_basic.R",ssl.verifypeer = FALSE)
eval(parse(text = script))
```

# 3. Demo

## 3.1 Simulating an endemic equilibrium without MDA

Before simulating treatment, the model must be simulated to the endemic equilibrium. It is best to run the model to equilibrium (```run_equilibrium = TRUE```, ```give.treat = 0 ```), save the output and use this as the starting point for MDA. Note that running the model to the equilibrium can be slow, taking in excess of 5 minutes (depending on machine performance). To run the model to equilibrium without treating in the same run, use the following code:

```{r, eval=F, echo = TRUE, collapse=TRUE}
#length of simulation in years
timesteps = 30

#should treatment be given, when and how often
give.treat.in = 0
treat.strt = 1; treat.stp = 16
trt.int = 1

#annual biting rate, which determines infection prevalence (60% microfilarae prevalence)
ABR.in = 1082

output_equilibrium <- ep.equi.sim(time.its = timesteps,
                                  ABR = ABR.in,
                                  N.in = 440,
                                  treat.int = trt.int,
                                  treat.prob = 0.65,
                                  give.treat = give.treat.in,
                                  treat.start = treat.strt,
                                  treat.stop = treat.stp,
                                  pnc = 0.05,
                                  min.mont.age = 5,
                                  delta.hz.in = 0.186,
                                  delta.hinf.in = 0.003,
                                  c.h.in = 0.005,
                                  gam.dis.in = 0.3,
                                  run_equilibrium = TRUE,
                                  equilibrium,
                                  print_progress = TRUE)
```

To stop the printing of the time as the model runs, set ```print_progress = FALSE```. If ```run_equilibrium = TRUE``` then no input is expected for ```equilibrium```, which is where a previously simulated endemic equilibrium can be entered. This will be discussed later in section 3.3. Above, no MDA is not requested by setting ```gv.trt = 0```. Note that values must be entered for treatment start, stop and interval (1 is annual, 0.5 is biannual), e.g ```treat.strt = 0; treat.stp = 16; trt.int = 1```, even if ```gv.trt = 0```.

## 3.2 Visualising microfilarial infection prevalence through time

The output from run_EPIONCHO_IBM is a list with four elements.

```{r, eval=T, echo=T, comment=NA}
names(output_equilibrium)
```

The first three elements contain the temporal dynamics (at 1 day increments) for the microfilarial prevalence (individuals age > 5), the population mean microfilarial intensity (individuals age > 5) and the mean number of L3 larvae in the black fly population. To plot these over time, use: 

```{r, eval=T, echo=T, comment=NA}
tme <- seq(1, 30*366-1)/366

plot(tme, output_equilibrium$mf_prev, type = 'l', xlab = 'time (years)', ylab = 'microfilarial prevalence', ylim = c(0, 1))

plot(tme, output_equilibrium$mf_intens, type = 'l', xlab = 'time (years)', ylab = 'mean microfilarial intensity')

plot(tme, output_equilibrium$L3, type = 'l', xlab = 'time (years)', ylab = 'mean L3 in fly population')
```

The fourth element,```"all_equilibrium_outputs"``` is the element required to simulate MDA without having to run the model to the endemic equilibrium.


## 3.3 Simulating annual and biannual mass drug administration with ivermectin
### 3.3.1 Annual MDA

Assuming you have already run the model and saved the output as described in section 3.1, you can simulate 15 years of annual mass drug administration with ivermectin by running:

```{r, eval=F, echo=T, comment=NA}
timesteps = 30 
treat.strt = 1; treat.stp = 26 #if model run stops in year 30, the last round is at the beginning of year 25
gv.trt = 1
trt.int = 1

output_treat_annual <- ep.equi.sim(time.its = timesteps,
                                   ABR = ABR.in,
                                   N.in = 440,
                                   treat.int = trt.int,
                                   treat.prob = 0.65,
                                   give.treat = gv.trt,
                                   treat.start = treat.strt,
                                   treat.stop = treat.stp,
                                   pnc = 0.05,
                                   min.mont.age = 5,
                                   delta.hz.in = 0.186,
                                   delta.hinf.in = 0.003,
                                   c.h.in = 0.005,
                                   gam.dis.in = 0.3,
                                   run_equilibrium = FALSE,
                                   equilibrium = output_equilibrium[[4]],
                                   print_progress = FALSE)

```

Above ```print_progress = FALSE```, but when ```gv.trt = 1```, the duration of MDA will be printed. Note that ```timesteps``` is the total number of years for which the model is run. ```treat.start``` and ```treat.stop``` are the years within this duration at which MDA is given.

To visualise the infection dynamics through time during annual MDA, use:

```{r, eval=T, echo=T, comment=NA}
tme <- seq(0, 30*366-1)/366

plot(tme, output_treat_annual$mf_prev, type = 'l', xlab = 'time', ylab = 'microfilarial prevalence', ylim = c(0, 1))

abline(v = seq(0, 30), col = 'black', lwd = 0.1)

plot(tme, output_treat_annual$mf_intens, type = 'l', xlab = 'time', ylab = 'mean microfilarial intensity')

abline(v = seq(0, 30), col = 'black', lwd = 0.1)
```

### 3.3.2 Biannual MDA

Assuming you have run the model to the endemic equilibrium (as described in secton 3.1), temporal infection trends during biannual MDA can be obtained by running:

```{r, eval=F, echo=T, comment=NA}
timesteps = 30 
treat.strt = 1; treat.stp = 26 #if treatment stops in year 16, the last round is at the beginning of year 15
gv.trt = 1
trt.int = 0.5


output_treat_biannual <- ep.equi.sim(time.its = timesteps,
                                   ABR = ABR.in,
                                   N.in = 440,
                                   treat.int = trt.int,
                                   treat.prob = 0.65,
                                   give.treat = gv.trt,
                                   treat.start = treat.strt,
                                   treat.stop = treat.stp,
                                   pnc = 0.05,
                                   min.mont.age = 5,
                                   delta.hz.in = 0.186,
                                   delta.hinf.in = 0.003,
                                   c.h.in = 0.005,
                                   gam.dis.in = 0.3,
                                   run_equilibrium = FALSE,
                                   equilibrium = output_equilibrium[[4]],
                                   print_progress = FALSE)

```

Note than above ```trt.int = 0.5``` (rather than ```trt.int = 1```) to request biannual MDA. The output can be visualised using:

```{r, eval=T, echo=T, comment=NA}
tme <- seq(0, 30*366-1)/366

plot(tme, output_treat_biannual$mf_prev, type = 'l', xlab = 'time', ylab = 'microfilarial prevalence', ylim = c(0, 1))

abline(v = seq(0, 30), col = 'black', lwd = 0.1)

plot(tme, output_treat_biannual$mf_intens, type = 'l', xlab = 'time', ylab = 'mean microfilarial intensity')

abline(v = seq(0, 30), col = 'black', lwd = 0.1)
```

### 3.3.3 Coverage and non-compliance

The population level coverage is a proportion and is entered via ```treat.prob```. Note that because children <5 do not receive treatment, coverage of 1 cannot be achieved. Additionally, there is the option to set the proportion of individuals who never take treatment (```pnc = 0.05```). 

### 4. References

1. R Core Team. R: A language and environment for statistical computing. (R Foundation for Statistical Computing, 2018).

2. Lang, D. T. & CRAN team. RCurl: General network (http/ftp/...) client interface for r. (2019).


