---
title: "Installing and Running EPIONCHO-IBM to output Ov16"
author:
- name: Aditya Ramani
  affiliation: Imperial College London, Royal Veterinary College
  role:         # Contributorship roles (e.g., CRediT)
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
  - Software
- name: Jacob Stapely
  affiliation: Imperial College London
  role:         
  - Conceptualization
- name: Jonathan Hamley
  affiliation: Imperial College London, University of Bern
  role:         # Contributorship roles (e.g., CRediT)
  - Conceptualization
- name: Martin Walker
  affiliation: Royal Veterinary College, Imperial College London
  role:         
  - Conceptualization
- name: Maria-Gloria Basanez
  affiliation: Imperial College London
  role:         
  - Conceptualization
date: "May 14, 2024"
output:
  html_document:
    df_print: paged
  word_document: default
  radix::radix_article: default
  pdf_document: default
description: |
  A stochastic, individual-based model for onchocerciasis transmission, now with serological outputs
---

**EPIONCH0-IBM is a stochastic, individual-based model for onchocerciasis transmission. A mathematical description can be found at https://doi.org/10.1371/journal.pntd.0007557.**

# 1. System requirements

EPIONCHO IBM is written in R (1) which is freely available for installation on Windows, Mac OS and Linux platforms from https://www.r-project.org. It is also recommended to install R Studio https://www.rstudio.com which provides a helpful user interface for R. EPIONCHO-IBM has been tested on Mac OS and Windows, but should be compatible with Linux and run on any desktop or laptop machine.

# 2. Installation guide

The model package can be downloaded and installed directly from a GitHub repository (https://github.com/adiramani/EPIONCHO.IBM). The remotes (2) package must be installed to do this. Installation should take no more than a few seconds on most desktop or laptop machines.


```{r, eval=T, echo = FALSE, collapse= FALSE}
remotes::install_github("adiramani/EPIONCHO.IBM")
library(EPIONCHO.IBM)
overall_start_time <- Sys.time()
```

# 3. Demo

The entire vignette should take ~30 minutes to run, with most of the time taken up by computational time.

## 3.1 Simulating to find ABR - mfp combinations

If you do not want to test out ABR values, skip to 3.3 to see how to simulate the model to get Ov16 outputs. This is also the most time consuming part of the vignette, as it takes ~12 minutes on average to compute.  
This is done by simulating the model to endemic equilibrium (which should occur by ~100 years of simulation). Note that running the model to the equilibrium can be slow, taking in excess of 5 minutes (depending on machine performance) per ABR/k~E. Parallel processing (not implemented below) can significantly decrease the run time. To reduce run-time, the code below will only test for 1 run of 2 ABRs for each kE value, over 50 years (typically we use 80-100 years). See section 3.1.1 for a parallel processing version with more ABRs, over a longer period of time. Use the following code to test the ABRs and k~E values tested for Gabon:

```{r, abr-mfp-sim}
time_start <- Sys.time()
num_iters_per_abr <- 1
abr_range_k2 <- seq(70, 79, 5)
abr_range_k3 <- seq(170, 179, 5)

abrs_k2 <- rep(abr_range_k2, num_iters_per_abr)
abrs_k3 <- rep(abr_range_k3, num_iters_per_abr)
all_abrs <- c(abrs_k2, abrs_k3)
total_sims <- length(all_abrs)
for(iter in 1:total_sims) {
  
  kEs = c(rep(0.2, length(abrs_k2)), rep(0.3, length(abrs_k3)))

  kE = kEs[iter]
  ABR.in <- all_abrs[iter]

  # Density dependent parameters based on the kE value chosen
  if(kE == 0.2) {
    delta.hz.in.val =  0.385
    delta.hinf.in.val = 0.003
    c.h.in.val = 0.008
    gam.dis.in.val = 0.2
  } else {
    delta.hz.in.val =  0.186
    delta.hinf.in.val = 0.003
    c.h.in.val = 0.005
    gam.dis.in.val = 0.3
  }

  # set the timestep for a year (iterate by 1 day, for a total of 366 days in a year)
  DT.in <- 1/366



  # total number of years of simulation (100)
  timesteps = 50

  # we don't want any MDA, but we still need to set a value for these in the model
  treat.strt = 0
  treat.stp = 1
  give.treat.in = 0; trt.int = 1; treat.prob.in = 0.80

  output <- ep.equi.sim(time.its = timesteps,
                        ABR = ABR.in,
                        treat.int = trt.int,
                        treat.prob = treat.prob.in,
                        give.treat = give.treat.in,
                        treat.start = treat.strt,
                        treat.stop = treat.stp,
                        treat.timing = NA,
                        pnc = 0.01,
                        # minimum age for skin-snipping
                        min.mont.age = 5,
                        vector.control.strt = NA,
                        delta.hz.in =  delta.hz.in.val,
                        delta.hinf.in = delta.hinf.in.val,
                        c.h.in = c.h.in.val,
                        gam.dis.in = gam.dis.in.val,
                        run_equilibrium = FALSE,
                        no_prev_run=TRUE,
                        print_progress=FALSE,
                        calc_ov16 = FALSE,
                        seroreversion="none")

  # save outputs for analysis
  params <- list(ABR.in, kE)
  names(params) <- c('ABR', 'Ke')
  output <- append(output, params)

  # be sure to make a folder called "test_output_folder"
  dir.create(file.path("test_output_folder/test_mfp_abr_output_folder/"), recursive=TRUE, showWarnings = FALSE)
  saveRDS(output, paste("test_output_folder/test_mfp_abr_output_folder/testing_mf_outputs", kE, "_", iter,".rds", sep=""))
}
paste("MFP Simulation Run Time", difftime(Sys.time(), time_start, units="mins"), "minutes")
```

To stop the printing of the time as the model runs, set ```print_progress = FALSE```. Currently, with ```print_progress = TRUE```, when the model run reaches each year in the simulation, the year and % progress will be printed.
Note that we set ```run_equilibrium = FALSE``` and  ```no_prev_run = TRUE```. While we are running to equilibrium, we are only doing so for the microfilarial prevalence outputs, and not for inputting the output into another model. Setting ```run_equilibrium = FALSE``` tells the model we only need the minimal output, and ```no_prev_run = TRUE``` lets the model know we have no previous input.
If you want to change the ABRs tested, and the number of times each ABR is run, you can adjust the following variables - 
```num_iters_per_abr```, ```abr_range_k2```, and ```abr_range_k3```

It is also possible to manually change the density-dependent parameters relating to the establishment of the adult *Onchocerca volvulus* (```delta.hz.in```, ```delta.hinf.in``` and ```c.h.in```) and individual exposure heterogeneity in humans (```gam.dis.in```), however they are set to be the fitted density-dependent parameters in [Hamley et al. 2019](https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0007557). 

### 3.1.1 Simulating with Parallel Processing

This section uses parallel (multi-core) processing to run multiple simulations at the same time. The general idea of the code is the same, however we use the [parallel](), [doParallel](), and [foreach]() packages to (```install.packages("parallel")```, ```install.packages("foreach")```, ```install.packages("doParallel")```) to run the simulations. The code below will be commented to explain the use of the parallel library. Note that the runtime will vary depending on the number of iterations, number of ABRs, and number of cores on your computer.

```{r, eval=FALSE, abr-mfp-sim-parallel}
library(doParallel)
library(foreach)
# this is just used to get the overal time of the
time_start <- Sys.time()

# set up ABRs to test
num_iters_per_abr <- 100
abr_range_k2 <- seq(70, 79, 5)
abr_range_k3 <- seq(170, 179, 5)

abrs_k2 <- rep(abr_range_k2, num_iters_per_abr)
abrs_k3 <- rep(abr_range_k3, num_iters_per_abr)
all_abrs <- c(abrs_k2, abrs_k3)
total_sims <- length(all_abrs)


# see how many cores are available
numCores = detectCores()
print(numCores)
# we want to leave at least 1 core free, but in case numCores is 1, we want to set the minimum to 1
coresToUse = max(1, numCores-1)
# a cluster is what we use to distribute and process our code in parallel. We need to initialize it with a number of cores to use
cl <- makeCluster(coresToUse)
# register the cluster to be used in doParallel
registerDoParallel(cl)


x <- foreach(
  i = 1:total_sims,
  .packages = c("EPIONCHO.IBM")
  ) %dopar% {

  kEs = c(rep(0.2, length(abrs_k2)), rep(0.3, length(abrs_k3)))
  
  kE = kEs[i]
  ABR.in <- all_abrs[i]

  # Density dependent parameters based on the kE value chosen
  if(kE == 0.2) {
    delta.hz.in.val =  0.385
    delta.hinf.in.val = 0.003
    c.h.in.val = 0.008
    gam.dis.in.val = 0.2
  } else {
    delta.hz.in.val =  0.186
    delta.hinf.in.val = 0.003
    c.h.in.val = 0.005
    gam.dis.in.val = 0.3
  }

  # set the timestep for a year (iterate by 1 day, for a total of 366 days in a year)
  DT.in <- 1/366



  # total number of years of simulation (100)
  timesteps = 100

  # we don't want any MDA, but we still need to set a value for these in the model
  treat.strt = 100
  treat.stp = 100
  give.treat.in = 0; trt.int = 1; treat.prob.in = 0.80

  output <- ep.equi.sim(time.its = timesteps,
                        ABR = ABR.in,
                        treat.int = trt.int,
                        treat.prob = treat.prob.in,
                        give.treat = give.treat.in,
                        treat.start = treat.strt,
                        treat.stop = treat.stp,
                        treat.timing = NA,
                        pnc = 0.01,
                        # minimum age for skin-snipping
                        min.mont.age = 5,
                        vector.control.strt = NA,
                        delta.hz.in =  delta.hz.in.val,
                        delta.hinf.in = delta.hinf.in.val,
                        c.h.in = c.h.in.val,
                        gam.dis.in = gam.dis.in.val,
                        run_equilibrium = FALSE,
                        no_prev_run=TRUE,
                        print_progress=FALSE,
                        calc_ov16 = FALSE,
                        seroreversion="none")

  # save outputs for analysis
  params <- list(ABR.in, kE)
  names(params) <- c('ABR', 'Ke')
  output <- append(output, params)

  # be sure to make a folder called "test_output_folder"
  dir.create(file.path("test_output_folder/test_mfp_abr_output_folder/"), recursive=TRUE, showWarnings = FALSE)
  saveRDS(output, paste("test_output_folder/test_mfp_abr_output_folder/testing_mf_outputs", kE, "_", iter,".rds", sep=""))
}
# stop the cluster (this is important, so other processes can use the nodes later)
stopCluster(cl)
print(paste("MFP Simulation Parallel Run Time", difftime(Sys.time(), time_start, units="mins"), "minutes"))
```

## 3.2 Visualising microfilarial infection prevalence by ABR

### 3.2.1 Processing outputs

To make visualisation easier, we need to process all of the outputs into a single dataframe. This step requires the `dplyr` package, which can be installed by running ```install.packages("dplyr")```
Note: This function below will be used in future steps for processing of the Ov16 Output.
```{r, processing-abr-mfp}
library(dplyr)
processOutputFiles <- function (fileToUse='test_output_folder/', location=0, verbose=TRUE, onlyCalcMFP=FALSE, useSerorevert=FALSE, onlyCalcOv16Trends=FALSE) {
  allOutputs <- data.frame()
  i <- 1
  mda_vals <- c()
  abr_vals <- c()
  mf_prev_vals <- c()
  total_files <- length(list.files(fileToUse))
  start_time <- Sys.time() 
  mf_prev_df <- matrix(ncol=4, nrow=0)
  ov16_trend_df <- matrix(ncol=4, nrow=0)
  for (file in list.files(fileToUse)) {
    if(verbose & total_files > 10) {
      if ((i %% floor(total_files/10)) == 0) {
        print(paste("Time Elapsed:", Sys.time()-start_time, ":", i / (total_files)))
        gc()
      }
    }
    tryCatch(
    {
      tmpRDSData <- readRDS(paste(fileToUse, file,sep=""))
    },
    error = function(e) {
      message(paste("Error occurred while reading:", fileToUse))
    }
    )
    
    mf_prev_vals <- c(mf_prev_vals, tail(tmpRDSData$mf_prev)[1])
    mda_vals <- c(mda_vals, tmpRDSData$MDA)
    abr_vals <- c(abr_vals, tmpRDSData$ABR)
    if(onlyCalcOv16Trends) {
      sero_prev_vals <- tmpRDSData$ov16_seroprevalence[c(1,seq(from=183, to=length(tmpRDSData$ov16_seroprevalence), by=183))]
      total_sero_vals <- length(sero_prev_vals)
      if(i == 1) {
        ov16_trend_df <- matrix(ncol=4, nrow=total_files*length(sero_prev_vals))
        colnames(ov16_trend_df) <- c("ABR", "Ke", "run_num", "ov16_vals")
      }
      ov16_trend_df[(1+(total_sero_vals*(i-1))):(i*total_sero_vals),1] <- rep(tmpRDSData$ABR, total_sero_vals)
      ov16_trend_df[(1+(total_sero_vals*(i-1))):(i*total_sero_vals),2] <- rep(tmpRDSData$Ke, total_sero_vals)
      ov16_trend_df[(1+(total_sero_vals*(i-1))):(i*total_sero_vals),3] <- rep(i,total_sero_vals)
      ov16_trend_df[(1+(total_sero_vals*(i-1))):(i*total_sero_vals),4] <- sero_prev_vals
      i <- i + 1
      next
    }
    if(onlyCalcMFP) {
      curr_mf_prev_vals <- tmpRDSData$mf_prev[c(1,seq(from=366, to=length(tmpRDSData$mf_prev), by=366))]
      total_mf_prev_vals <- length(curr_mf_prev_vals)
      if(i == 1) {
        mf_prev_df <- matrix(ncol=4, nrow=total_files*total_mf_prev_vals)
        colnames(mf_prev_df) <- c("ABR", "Ke", "run_num", "mf_prev")
      }
      mf_prev_df[(1+(total_mf_prev_vals*(i-1))):(i*total_mf_prev_vals),1] <- rep(tmpRDSData$ABR, total_mf_prev_vals)
      mf_prev_df[(1+(total_mf_prev_vals*(i-1))):(i*total_mf_prev_vals),2] <- rep(tmpRDSData$Ke, total_mf_prev_vals)
      mf_prev_df[(1+(total_mf_prev_vals*(i-1))):(i*total_mf_prev_vals),3] <- rep(i, total_mf_prev_vals)
      mf_prev_df[(1+(total_mf_prev_vals*(i-1))):(i*total_mf_prev_vals),4] <- curr_mf_prev_vals
      i <- i + 1
      next
    }
    
    matrix_to_use <- tmpRDSData$ov16_seropositive_matrix
    if(useSerorevert) {
      matrix_to_use <- tmpRDSData$ov16_seropositive_matrix_serorevert
    }
    
    age <- matrix_to_use[, 1 + (location*i)]
    sex <- ifelse(matrix_to_use[,2 + (location*i)] == 1, "Male", "Female")
    mf_prev <- matrix_to_use[,3 + (location*i)]
    ov16_seropos <- matrix_to_use[,4 + (location*i)]
    ov_l3 <- matrix_to_use[,5 + (location*i)]
    ov_l4 <- matrix_to_use[,6 + (location*i)]
    ov_mating_no_mf <- matrix_to_use[,7 + (location*i)]
    ov_mating_detectable_mf <- matrix_to_use[,8 + (location*i)]
    ov_mating_any_mf <- matrix_to_use[,9 + (location*i)]

    tmpNumRows <- length(age)
    if(i == 1) {
      if(useSerorevert) {
        allOutputs <- data.frame(matrix(ncol=13, nrow=tmpNumRows*total_files))
        colnames(allOutputs) <- c("age", "sex", "ov16_pos", "ov16_pos_l3", "ov16_pos_l4", "ov16_pos_mating_no_mf", "ov16_pos_mating_detectable_mf", "ov16_pos_mating_any_mf", "mf_prev", "ABR", "Ke", "sero_type", "run_num")
      } else {
        allOutputs <- data.frame(matrix(ncol=12, nrow=tmpNumRows*total_files))
        colnames(allOutputs) <- c("age", "sex", "ov16_pos", "ov16_pos_l3", "ov16_pos_l4", "ov16_pos_mating_no_mf", "ov16_pos_mating_detectable_mf", "ov16_pos_mating_any_mf", "mf_prev", "ABR", "Ke", "run_num")
      }
    }

    startIndex <- 1+tmpNumRows*(i-1)
    endIndex <- tmpNumRows*i
    if(useSerorevert) {
        allOutputs[startIndex:endIndex,-13] <- list(age, sex, ov16_seropos, ov_l3, ov_l4, ov_mating_no_mf, ov_mating_detectable_mf, ov_mating_any_mf, mf_prev, rep(tmpRDSData$ABR, tmpNumRows), rep(tmpRDSData$Ke, tmpNumRows), rep(tmpRDSData$sero_type, tmpNumRows))
        allOutputs[startIndex:endIndex,13] <- i
    } else {
        allOutputs[startIndex:endIndex,-12] <- list(age, sex, ov16_seropos, ov_l3, ov_l4, ov_mating_no_mf, ov_mating_detectable_mf, ov_mating_any_mf, mf_prev, rep(tmpRDSData$ABR, tmpNumRows), rep(tmpRDSData$Ke, tmpNumRows))
        allOutputs[startIndex:endIndex,12] <- i
    }

    i <- i + 1
  }

  if(onlyCalcOv16Trends) {
    ov16Return <- list(ov16_trend_df)
    names(ov16Return) <- c("ov16_trend_df")
    return(ov16Return)
  }

  if(onlyCalcMFP) {
    mfpReturn <- list(mf_prev_df, mf_prev_vals, mda_vals, abr_vals)
    names(mfpReturn) <- c("mf_prev_df", 'mf_prev', 'mda_vals', 'abr_vals')
    return(mfpReturn)
  }

  allOutputs <- allOutputs %>% mutate(
                                      age_groups = case_when(
                                                ceiling(age*5)/5 == 0 ~ 0,
                                                age <= 75 ~ ceiling(age/5)*5 - 2.5,
                                                TRUE ~ 77.5
                                              )
                                      )
  returnVal <- list(allOutputs, mf_prev_vals, abr_vals, mda_vals)
  names(returnVal) <- c("allOutputs", "mf_prev", "abr_vals", "mda_vals")
  return(returnVal)
}
saveRDS(processOutputFiles(file="test_output_folder/test_mfp_abr_output_folder/", onlyCalcMFP = TRUE), "test_output_folder/mfp_abr_all_age_data.RDS")
```

### 3.2.2 Visualising Output

Now that we have the abrs, k~E~s, and mfp values combined into a single dataframe, we can run the following code to visualize the ABR-k~E~ microfilarial prealence trends (Note: This step requires the `dplyr` and ggplot2 packages, which can be installed by running ```install.packages("dplyr")``` and ```install.packages("ggplot2")```):

```{r, visualising-mfp-abr}
library(ggplot2)
library(dplyr)
# load dataframe, and add a time column (each datapoint for a run constitutes a year in that run)
gabon_mfp_data_df <- readRDS("test_output_folder/mfp_abr_all_age_data.RDS")$mf_prev_df %>% as.data.frame() %>% group_by(ABR, Ke, run_num) %>% mutate(time = row_number()) %>% ungroup()

# grouped by ABR, kE and time, find the mean MFP across all runs for that combination, and then filter it out to get the MFP at the last year
gabon_mfp_data_df_mutated <- gabon_mfp_data_df %>% group_by(ABR, Ke, time) %>% summarize(mean_mfp = mean(mf_prev)*100, .groups="drop") %>% filter(time == max(time))

mfp_vs_abr_plot <- ggplot(data=gabon_mfp_data_df_mutated) + 
  geom_point(aes(x=ABR, y=mean_mfp)) +
  facet_wrap(~ Ke, scales = "free_x") +
  ylab("Mean Microfilarial Prevalence (%) at Equilibrium") +
  labs(
    title = expression("k"["E"])
  ) +
  scale_color_manual("Observed Microfilarial Prevalence 95% CI", values=c("black", "red")) +
  theme_bw() +
  theme(
    plot.title = element_text(size=10, hjust = 0.5),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )
mfp_vs_abr_plot
```

## 3.3 Simulating for Ov16 seroprevalence outputs

This section will explain how to output Ov16 seroprevalence in the model, with the following hypotheses:
1) L3 Exposure
2) During L4-L5 Moult
3) In the presence of Any Adult Worm
4) With a mating worm pair and any (modelled) microfilarae
5) With a mating worm pair
6) With a mating worm pair and detectable (via skin-snips) microfilarae

Only hypotheses 1-3, and 5 were present in the paper. Hypotheses 5 and 6 were removed as they both cover the same biological process as hypothesis 4.

### 3.3.1 No MDA

To output Ov16 values for all hypotheses in a scenario where there is no MDA, we can do the same thing as we did in step 3.1, just setting ```calc_ov16 = TRUE```.
If you want to include seroreversion, you can set the `sero.in`/`seroreversion` parameter to `"no_infection"` or `"absence_of_trigger"`. 
The model is set to output at the last timestep by default (if no MDA is applied). If you want to customize the times at which the seroprevalence is output, you can add the parameter ```ov16_store_times = c(x...)```, which will set the store times to be at the year you input. For example ```ov16_store_times = c(50, 100)``` will output data at year 50 and 100.
Note: To simplify the code, we are doing 1 run, with a k~E~ of 0.2, and an ABR of 72, but for consistant results, you would need to simulate this at least 1000 times (this value has not been strictly tested) and calculate the mean Ov16 seroprevalence.

```{r, no-mda-ov16-sim}
kE = 0.2
sero.in <- "none"

# Density dependent parameters based on a kE of 0.2
delta.hz.in.val =  0.385
delta.hinf.in.val = 0.003
c.h.in.val = 0.008
gam.dis.in.val = kE

# Set ABR
ABR.in <- 72

# set the timestep for a year (iterate by 1 day, for a total of 366 days in a year)
DT.in <- 1/366

# total number of years of simulation (100)
timesteps = 100

# we don't want any MDA, but we still need to set a value for these in the model
treat.strt = 100
treat.stp = 100
give.treat.in = 0; trt.int = 1; treat.prob.in = 0.80

output <- ep.equi.sim(time.its = timesteps,
                      ABR = ABR.in,
                      treat.int = trt.int,
                      treat.prob = treat.prob.in,
                      give.treat = give.treat.in,
                      treat.start = treat.strt,
                      treat.stop = treat.stp,
                      treat.timing = NA,
                      pnc = 0.01,
                      # minimum age for skin-snipping
                      min.mont.age = 5,
                      vector.control.strt = NA,
                      delta.hz.in =  delta.hz.in.val,
                      delta.hinf.in = delta.hinf.in.val,
                      c.h.in = c.h.in.val,
                      gam.dis.in = gam.dis.in.val,
                      run_equilibrium = FALSE,
                      no_prev_run=TRUE,
                      print_progress=TRUE,
                      calc_ov16 = TRUE,
                      seroreversion=sero.in)

# save outputs for analysis
params <- list(ABR.in, kE, sero.in)
names(params) <- c('ABR', 'Ke', "sero_type")
output <- append(output, params)

# be sure to make a folder called "test_ov16_no_mda_output_folder"
dir.create(file.path("test_output_folder/test_ov16_no_mda_output_folder/"), recursive=TRUE, showWarnings = FALSE)
saveRDS(output, paste("test_output_folder/test_ov16_no_mda_output_folder/testing_no_mda_outputs", kE, "_", iter,".rds", sep=""))
```

The main value of the `output` that will have the seroprevalence values is `ov16_seropositive_matrix` (or `ov16_seropositive_matrix_serorevert` if you used seroreversion). This is a matrix with N x (9*i) rows, with N being the number of individuals in the population. The number of columns is a multiple of 9, defined by i, where i is the number of output times in `ov16_store_times`.
The columns (by index) contain the following information for the given individual in that row:
Column:
1 - Age
2 - Sex (1 = Male)
3 - Skin Snip Result
4 - OV16 Seroprevalence (Hypothesis 3)
5 - OV16 Seroprevalence (Hypothesis 1)
6 - OV16 Seroprevalence (Hypothesis 2)
7 - OV16 Seroprevalence (Hypothesis 5)
8 - OV16 Seroprevalence (Hypothesis 6)
9 - OV16 Seroprevalence (Hypothesis 4)

The order of the columns will always be the same, and in the case of multiple timesteps of output, will be ordered by the earliest output.
I.e: with ```ov16_store_times = c(50, 100)```, column 1 = age at year 50, column 10 = age at year 100, etc. 

#### 3.3.1.1 Visualising the Age Stratified Ov16 seroprevalence by Hypothesis

We can use the same function that we used in 3.2.2 to process the data, before visualizing it. We adjust the simulation data using the OEPA ELISA, but feel free to change it as you wish in the code below.
This step requires the package dplyr, tidyr, and ggplot2, which can be installed by running ```install.packages("ggplot2")```, ```install.packages("dplyr")```, and ```install.packages("tidyr")``` if they are not already installed.

```{r, no-mda-ov16-age-vis}
library(dplyr)
library(ggplot2)
library(tidyr)
# process data
seroprevalence_data <- processOutputFiles(file="test_output_folder/test_ov16_no_mda_output_folder/")$allOutputs
# if you used seroreversion, run this instead
# seroprevalence_data <- processOutputFiles(file="test_output_folder/test_ov16_no_mda_output_folder/", useSerorevert=TRUE)$allOutputs
# if you used multiple timepoints, you need to set the `location` parameter to match the output time you want to look at.
# The first output time corresponds to location = 0, second output time to location = 1, etc.
# seroprevalence_data <- processOutputFiles(file="test_output_folder/test_ov16_no_mda_output_folder/", location=1)$allOutputs


# data explanation: 
# each row signifies an individual
# ov16_pos_l3 - ov16 status for hypothesis 1
# ov16_pos_l4 - ov16 status for hypothesis 2
# ov16_pos - ov16 status for hypothesis 3
# ov16_pos_mating_any_mf - ov16 status for hypothesis 4
# ov16_pos_mating_no_mf - ov16 status for hypothesis 5
# ov16_pos_mating_detectable_mf - ov16 status for hypothesis 6
# mf_prev - mf skin snip status for an individual
# ABR - ABR for the run the individual was a part of
# Ke - kE for the run the individual was a part of
# run_num - unique run number
# age_groups - age_group of individuals (5 year bins)
names(seroprevalence_data)

# adjust for sensitivity and specificity
# this is a helper function to calculate the sensitivity and specificity
calcSensSpecSeroPrev <- function(run_seropos_data, sens=1, spec=1, prob=c()) {
  indv <- length(run_seropos_data)
  if(length(prob) < indv) {
    prob <- runif(indv)
  }
  
  if(length(sens) ==0 | is.na(sens)) {
    sens <- 1
  }
  if(length(sens) == 0 | is.na(spec)) {
    spec <- 1
  }
  
  new_seropos_data<-rep(0, indv)
  pos <- which(run_seropos_data==1)
  neg <- which(run_seropos_data==0)

  if(length(pos) > 0) {
    new_seropos_data[pos] <- as.numeric(prob[pos] <= sens)
  }
  if(length(neg) > 0) {
    new_seropos_data[neg] <- as.numeric(prob[neg] > spec)
  }
  return(new_seropos_data)
}

# from OEPA ELISA; feel free to edit it
sens = 0.43; spec = 0.998
seroprevalence_data$probs <- runif(dim(seroprevalence_data)[1])
seroprevalence_data_adj <- seroprevalence_data %>% group_by(run_num) %>%
  mutate(
          ov16_pos_l3=calcSensSpecSeroPrev(ov16_pos_l3, sens, spec, probs),
          ov16_pos_l4=calcSensSpecSeroPrev(ov16_pos_l4, sens, spec, probs),
          ov16_pos=calcSensSpecSeroPrev(ov16_pos, sens, spec, probs),
          ov16_pos_mating_detectable_mf=calcSensSpecSeroPrev(ov16_pos_mating_detectable_mf, sens, spec, probs),
          ov16_pos_mating_no_mf=calcSensSpecSeroPrev(ov16_pos_mating_no_mf, sens, spec, probs),
          ov16_pos_mating_any_mf=calcSensSpecSeroPrev(ov16_pos_mating_any_mf, sens, spec, probs)
        ) %>% ungroup() %>% as.data.frame()

# find average seroprevalence by age group
seroprevalence_data_adj <- seroprevalence_data_adj %>% group_by(run_num, age_groups) %>% summarise(
                     ov16_l3_prev=mean(ov16_pos_l3),
                     ov16_l4_prev=mean(ov16_pos_l4),
                     ov16_any_worm_prev=mean(ov16_pos),
                     ov16_mating_any_mf_prev=mean(ov16_pos_mating_any_mf),
                     ov16_mating_no_mf_prev=mean(ov16_pos_mating_no_mf),
                     ov16_mating_detectable_mf_prev=mean(ov16_pos_mating_detectable_mf),
                     mf_prev=mean(mf_prev), .groups="drop") %>% as.data.frame()
# Name the hypotheses
colnames(seroprevalence_data_adj)[all_of(3:8)] <- list("L3 exposure", "L4-L5 moult", "Any worm", "Mating worm pair with any mf", "Mating worm pair", "Mating worm pair with detectable mf")

# Calculate Mean
seroprevalence_data_summary <- seroprevalence_data_adj %>%
  as.data.frame() %>% pivot_longer(cols=all_of(3:8), names_to="Hypothesis", values_to = "ov16_prev") %>%
  group_by(age_groups, Hypothesis) %>%
  summarise(
    ov16_q1 = quantile(ov16_prev, probs=0.25),
    ov16_q3 = quantile(ov16_prev, probs=0.75),
    ov16_prev=mean(ov16_prev), 
    mf_q1 = quantile(mf_prev, probs=0.25),
    mf_q3 = quantile(mf_prev, probs=0.75),
    mf_prev=mean(mf_prev), .groups="drop") %>% as.data.frame()

# plot the data
plot <- ggplot() +
    geom_line(aes(x=age_groups, y=ov16_prev*100, color=Hypothesis), linewidth=1.1, data=seroprevalence_data_summary) +    
    scale_color_manual(name="Hypotheses", 
                       values=c("Any worm"="blue", "Any Adult worm"="blue", "L3 exposure"="purple", "L4-L5 moult"="#6366f2", "Mating worm pair"="brown", "Mating worm pair with any mf"="red", "Mating worm pair with detectable mf"="orange")) +
    theme_bw() +
    xlab("Age (years)") +
    ylab("Ov16 Seroprevalence (%)")
plot
```

#### 3.3.1.2 Time trends

You can look at the time trend of Ov16 seroprevalence as well, however it is only output with the best fit hypothesis, and without diagnostic adjustment (Hypothesis 4). 
This step requires the package dplyr and ggplot2, which can be installed by running ```install.packages("ggplot2")``` and ```install.packages("dplyr")```, if they are not already installed.
```{r, no-mda-ov16-time-vis}
library(dplyr)
library(ggplot2)
sero_trend <- as.data.frame(processOutputFiles(file="test_output_folder/test_ov16_no_mda_output_folder/", onlyCalcOv16Trends=TRUE)$ov16_trend_df) %>% group_by(Ke, run_num) %>% mutate(time = (row_number()/2)) %>% ungroup()

mfp_trend <- as.data.frame(processOutputFiles(file="test_output_folder/test_ov16_no_mda_output_folder/", onlyCalcMFP=TRUE)$mf_prev_df) %>% group_by(Ke, run_num) %>% mutate(time = row_number()) %>% ungroup()

time_plot <- ggplot() + geom_line(
  data=mfp_trend %>% group_by(time) %>% summarize(prev=mean(mf_prev), .groups="drop"),
  aes(x=time, y=prev*100, color="MF Prevalence")) + 
  geom_line(
    data=sero_trend %>% group_by(time) %>% summarize(prev=mean(ov16_vals), .groups="drop"),
    aes(x=time, y=prev*100, color="Ov16 Seroprevalence")
  ) +
  scale_y_continuous("Prevalence (%)", breaks=seq(0, 100, 10)) +
  theme_bw()
time_plot
```

### 3.3.2 Applying Complex MDA

To exemplify using Complex MDA, we will go over the simulations for Keran. For the full code on the Togo simulations, look at the file `all_funcs_combined_togo.R`
```{r, mda-ov16-sim}
kE = 0.3
sero.in <- "none"

delta.hz.in.val =  0.186
delta.hinf.in.val = 0.003
c.h.in.val = 0.005
gam.dis.in.val = kE

vctr.control.strt <- 80
vctr.control.duration <- 31
vctr.control.efficacy <- 0.75

prefecture = "keran"
ABR.in <- round(rgamma(1, 12.28, .0014)) # ~85%

# treat.strt.yrs 93 matches with 1989
treat.len = 26; treat.strt.yrs = 93; yrs.post.treat = 1

treat.strt = treat.strt.yrs; treat.stp = treat.strt + treat.len; 
timesteps = treat.stp + yrs.post.treat #final duration

# custom treatment parameters to apply intervention that varies over the years 
cstm_treat_params <- list(start_biannual=treat.strt.yrs+14, coverage_changes=c(treat.strt.yrs+7, treat.strt.yrs+14), coverage_change_values=c(0.55, 0.75, 0.85))
# If you want to apply a constant intervention, uncomment the following line, and set the desired value for treat.prob.in and pnc.in
# cstm_treat_params = list()
treat.prob.in=0.80 # this is overridden by cstm_treat_params, if it exists
# percent of population not treated
pnc.in = 0.01


give.treat.in = 1; trt.int = 1

output <- ep.equi.sim(time.its = timesteps,
                      ABR = ABR.in,
                      treat.int = trt.int,
                      treat.prob = treat.prob.in,
                      give.treat = give.treat.in,
                      treat.start = treat.strt,
                      treat.stop = treat.stp,
                      treat.timing = NA,
                      pnc = pnc.in,
                      min.mont.age = 5,
                      vector.control.strt = vctr.control.strt,
                      vector.control.duration = vctr.control.duration,
                      vector.control.efficacy = vctr.control.efficacy,
                      delta.hz.in =  delta.hz.in.val,
                      delta.hinf.in = delta.hinf.in.val,
                      c.h.in = c.h.in.val,
                      gam.dis.in = gam.dis.in.val,
                      N.in = 500,
                      run_equilibrium = FALSE,
                      print_progress=TRUE,
                      calc_ov16 = TRUE,
                      no_prev_run=TRUE,
                      custom_treat_params=cstm_treat_params,
                      seroreversion=sero.in)

params <- list(ABR.in, kE, sero.in, vctr.control.efficacy)
names(params) <- c('ABR', 'Ke', "sero_type", "vctr.ctrl.eff")
output <- append(output, params)

# be sure to create a folder called "test_ov16_mda_output_folder"
dir.create(file.path("test_output_folder/test_ov16_mda_output_folder/"), recursive=TRUE, showWarnings = FALSE)
saveRDS(output, paste("test_output_folder/test_ov16_mda_output_folder/ov16_output_togo_", prefecture, "_", kE,".rds", sep=""))
```

#### 3.3.2.1 Visualising

We can use the same process as 3.3.1.1 to visualize the output. 
This step requires the package dplyr, tidyr, and ggplot2, which can be installed by running ```install.packages("ggplot2")```, ```install.packages("dplyr")```, and ```install.packages("tidyr")``` if they are not already installed.

```{r, mda-ov16-age-vis}
library(dplyr)
library(ggplot2)
library(tidyr)
# process data
seroprevalence_data_mda <- processOutputFiles(file="test_output_folder/test_ov16_mda_output_folder/")$allOutputs
# if you used seroreversion, uncomment the line below
# seroprevalence_data_mda <- processOutputFiles(file="test_output_folder/test_ov16_mda_output_folder/", useSerorevert=TRUE)$allOutputs
# if you used multiple timepoints, you need to set the `location` parameter to match the output time you want to look at.
# The first output time corresponds to location = 0, second output time to location = 1, etc.
# seroprevalence_data_mda <- processOutputFiles(file="test_output_folder/test_ov16_mda_output_folder/", location=1)$allOutputs


# data explanation: 
# each row signifies an individual
# ov16_pos_l3 - ov16 status for hypothesis 1
# ov16_pos_l4 - ov16 status for hypothesis 2
# ov16_pos - ov16 status for hypothesis 3
# ov16_pos_mating_any_mf - ov16 status for hypothesis 4
# ov16_pos_mating_no_mf - ov16 status for hypothesis 5
# ov16_pos_mating_detectable_mf - ov16 status for hypothesis 6
# mf_prev - mf skin snip status for an individual
# ABR - ABR for the run the individual was a part of
# Ke - kE for the run the individual was a part of
# run_num - unique run number
# age_groups - age_group of individuals (5 year bins)
names(seroprevalence_data_mda)

# adjust for sensitivity and specificity
# this is a helper function to calculate the sensitivity and specificity
calcSensSpecSeroPrev <- function(run_seropos_data, sens=1, spec=1, prob=c()) {
  indv <- length(run_seropos_data)
  if(length(prob) < indv) {
    prob <- runif(indv)
  }
  
  if(length(sens) ==0 | is.na(sens)) {
    sens <- 1
  }
  if(length(sens) == 0 | is.na(spec)) {
    spec <- 1
  }
  
  new_seropos_data<-rep(0, indv)
  pos <- which(run_seropos_data==1)
  neg <- which(run_seropos_data==0)

  if(length(pos) > 0) {
    new_seropos_data[pos] <- as.numeric(prob[pos] <= sens)
  }
  if(length(neg) > 0) {
    new_seropos_data[neg] <- as.numeric(prob[neg] > spec)
  }
  return(new_seropos_data)
}

# from OEPA ELISA
sens = 0.43; spec = 0.998
seroprevalence_data_mda$probs <- runif(dim(seroprevalence_data_mda)[1])
seroprevalence_data_mda_adj <- seroprevalence_data_mda %>% group_by(run_num) %>%
  mutate(
          ov16_pos_l3=calcSensSpecSeroPrev(ov16_pos_l3, sens, spec, probs),
          ov16_pos_l4=calcSensSpecSeroPrev(ov16_pos_l4, sens, spec, probs),
          ov16_pos=calcSensSpecSeroPrev(ov16_pos, sens, spec, probs),
          ov16_pos_mating_detectable_mf=calcSensSpecSeroPrev(ov16_pos_mating_detectable_mf, sens, spec, probs),
          ov16_pos_mating_no_mf=calcSensSpecSeroPrev(ov16_pos_mating_no_mf, sens, spec, probs),
          ov16_pos_mating_any_mf=calcSensSpecSeroPrev(ov16_pos_mating_any_mf, sens, spec, probs)
        ) %>% ungroup() %>% as.data.frame()

# find average seroprevalence by age group
seroprevalence_data_mda_adj <- seroprevalence_data_mda_adj %>% group_by(run_num, age_groups) %>% summarise(
                     ov16_l3_prev=mean(ov16_pos_l3),
                     ov16_l4_prev=mean(ov16_pos_l4),
                     ov16_any_worm_prev=mean(ov16_pos),
                     ov16_mating_any_mf_prev=mean(ov16_pos_mating_any_mf),
                     ov16_mating_no_mf_prev=mean(ov16_pos_mating_no_mf),
                     ov16_mating_detectable_mf_prev=mean(ov16_pos_mating_detectable_mf),
                     mf_prev=mean(mf_prev), .groups="drop") %>% as.data.frame()
# Name the hypotheses
colnames(seroprevalence_data_mda_adj)[all_of(3:8)] <- list("L3 exposure", "L4-L5 moult", "Any worm", "Mating worm pair with any mf", "Mating worm pair", "Mating worm pair with detectable mf")

# Calculate Mean
seroprevalence_data_mda_summary <- seroprevalence_data_mda_adj %>%
  as.data.frame() %>% pivot_longer(cols=all_of(3:8), names_to="Hypothesis", values_to = "ov16_prev") %>%
  group_by(age_groups, Hypothesis) %>%
  summarise(
    ov16_q1 = quantile(ov16_prev, probs=0.25),
    ov16_q3 = quantile(ov16_prev, probs=0.75),
    ov16_prev=mean(ov16_prev), 
    mf_q1 = quantile(mf_prev, probs=0.25),
    mf_q3 = quantile(mf_prev, probs=0.75),
    mf_prev=mean(mf_prev), .groups="drop") %>% as.data.frame()

# plot the data
plot_mda <- ggplot() +
    geom_line(aes(x=age_groups, y=ov16_prev*100, color=Hypothesis), linewidth=1.1, data=seroprevalence_data_mda_summary) +    
    scale_color_manual(name="Hypotheses", 
                       values=c("Any worm"="blue", "Any Adult worm"="blue", "L3 exposure"="purple", "L4-L5 moult"="#6366f2", "Mating worm pair"="brown", "Mating worm pair with any mf"="red", "Mating worm pair with detectable mf"="orange")) +
    theme_bw() +
    xlab("Age (years)") +
    ylab("Ov16 Seroprevalence (%)")
plot_mda
```

#### 3.3.2.2 Time trends

We can use the same process as 3.3.1.2 to visualize the output. 
This step requires the package dplyr and ggplot2, which can be installed by running ```install.packages("ggplot2")``` and ```install.packages("dplyr")```, if they are not already installed..

```{r, mda-ov16-time-vis}
library(dplyr)
library(ggplot2)
sero_trend_mda <- as.data.frame(processOutputFiles(file="test_output_folder/test_ov16_mda_output_folder/", onlyCalcOv16Trends=TRUE)$ov16_trend_df) %>% group_by(Ke, run_num) %>% mutate(time = (row_number()/2)) %>% ungroup()

mfp_trend_mda <- as.data.frame(processOutputFiles(file="test_output_folder/test_ov16_mda_output_folder/", onlyCalcMFP=TRUE)$mf_prev_df) %>% group_by(Ke, run_num) %>% mutate(time = row_number()) %>% ungroup()

time_plot_mda <- ggplot() + geom_line(
  data=mfp_trend_mda %>% group_by(time) %>% summarize(prev=mean(mf_prev), .groups="drop"),
  aes(x=time, y=prev*100, color="MF Prevalence")) + 
  geom_line(
    data=sero_trend_mda %>% group_by(time) %>% summarize(prev=mean(ov16_vals), .groups="drop"),
    aes(x=time, y=prev*100, color="Ov16 Seroprevalence")
  ) +
  scale_y_continuous("Prevalence (%)", breaks=c(seq(0, 100, 10))) +
  theme_bw()
time_plot_mda
print(paste("Overall Vignette Run time: ", difftime(Sys.time(), time_start, units="mins"), "minutes"))
```

### 4. Cleaning up Data

Use this code to clean up the artifacts made from running this code.

```{r, clean-up}
unlink("test_output_folder/", recursive = TRUE)
```
### 5. References

1. R Core Team. R: A language and environment for statistical computing. (R Foundation for Statistical Computing, 2018).

2. Csárdi, G. RCurl: Package ‘remotes’: R Package Installation from Remote Repositories, Including 'GitHub'. (2022). https://cran.r-project.org/web/packages/remotes/ 


