---
title: "Running complex interventions in EPIONCHO-IBM"
author:
- name: Matthew A Dixon
  affiliation: Imperial College London, SCI Foundation 
  role:       # Contributorship roles (e.g., CRediT)   
  - Software
  - Data/ code curation 
- name: Jonathan Hamley
  affiliation: Imperial College London, University of Bern
  role:        
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
  - Software
- name: Martin Walker
  affiliation: Royal Veterinary College, Imperial College London
  role:         
  - Conceptualization
  - Software

date: "Febuary 14, 2023"
output:
  html_document:
    df_print: paged
  word_document: default
  radix::radix_article: default
  pdf_document: default
description: |
  A stochastic, individual-based model for onchocerciasis transmission
---

**EPIONCH0-IBM is a stochastic, individual-based model for onchocerciasis transmission. A mathematical description can be found at https://doi.org/10.1371/journal.pntd.0007557.**

# 1. System requirements

EPIONCHO IBM is written in R (1) which is freely available for installation on Windows, Mac OS and Linux platforms from https://www.r-project.org. It is also recommended to install R Studio https://www.rstudio.com which provides a helpful user interface for R. EPIONCHO-IBM has been tested on Mac OS and Windows, but should be compatible with Linux and run on any desktop or laptop machine.

# 2. Installation guide

The model package can be downloaded and installed directly from a GitHub repository (https://github.com/mrc-ide/EPIONCHO.IBM). The remotes (2) package must be installed to do this. Installation should take no more than a few seconds on most desktop or laptop machines.


```{r, eval=T, echo = FALSE, collapse= FALSE}
remotes::install_github("mrc-ide/EPIONCHO.IBM")
library(EPIONCHO.IBM)
```

# 3. Demo

## 3.1 Simulating an endemic equilibrium without MDA

As in the previous vignette, before simulating treatment, the model can be simulated to the endemic equilibrium. It is best to run the model to equilibrium (```run_equilibrium = TRUE```, ```give.treat = 0 ```), save the output and use this as the starting point for MDA. Note that running the model to the equilibrium can be slow, taking in excess of 5 minutes (depending on machine performance). To run the model to equilibrium without treating in the same run, use the following code:

```{r}
#length of simulation in years
timesteps = 30

#should treatment be given, when and how often
give.treat.in = 0
treat.strt = 1; treat.stp = 16
trt.int = 1

#annual biting rate, which determines infection prevalence (60% microfilarae prevalence)
ABR.in = 1082

output_equilibrium <- ep.equi.sim(time.its = timesteps,
                                  ABR = ABR.in,
                                  N.in = 440,
                                  treat.int = trt.int,
                                  treat.prob = 0.65,
                                  give.treat = give.treat.in,
                                  treat.start = treat.strt,
                                  treat.stop = treat.stp,
                                  pnc = 0.05,
                                  min.mont.age = 5,
                                  vector.control.strt = NA,
                                  delta.hz.in = 0.186,
                                  delta.hinf.in = 0.003,
                                  c.h.in = 0.005,
                                  gam.dis.in = 0.3,
                                  run_equilibrium = TRUE,
                                  equilibrium,
                                  print_progress = TRUE)
```

To stop the printing of the time as the model runs, set ```print_progress = FALSE```. Currently, with ```print_progress = TRUE```, when the model run reaches each year in the simulation, the year and % progress will be printed. For full details of inputs used in the ```ep.equi.sim``` function for endemic equilibrium runs, please see the introductory vignette: [Installing and Running EPIONCHO-IBM](https://github.com/mrc-ide/EPIONCHO.IBM/blob/master/vignettes/Running_EPIONCHO_IBM.Rmd). 

The fourth element,```"all_equilibrium_outputs"``` is the element required to simulate MDA without having to run the model to the endemic equilibrium.


## 3.2 Simulating more complex interventions: variable coverage and frequency of mass drug administration with ivermectin

### 3.2.1 Variable MDA coverage

Assuming you have already run the model and saved the output as described in section 3.1, you can simulate 25 years of annual mass drug administration with ivermectin with different coverage values at each round by running:

```{r}
timesteps = 30
treat.strt = 1; treat.stp = 26 #if model run stops in year 30, the last round is at the beginning of year 25
gv.trt = 1
trt.int = 1

treat.prob.variable.in <- c(0.65, 0.75, 0.5, 0.85, 0.9, 0.85, 0.5, 0.65, 0.9, 0.8, 0.6, 0.7, 0.95, 0.9, 0.95, 0.6, 0.5,
                            0.8, 0.85, 0.9, 0.95, 0.9, 0.9, 0.85, 0.85) # this is vector of variable coverages at each round

output_treat_annual <- ep.equi.sim(time.its = timesteps,
                                   ABR = ABR.in,
                                   N.in = 440,
                                   treat.timing = NA,
                                   treat.int = trt.int,
                                   treat.prob.variable = treat.prob.variable.in,
                                   give.treat = gv.trt,
                                   treat.start = treat.strt,
                                   treat.stop = treat.stp,
                                   pnc = 0.05,
                                   min.mont.age = 5,
                                   vector.control.strt = NA,
                                   delta.hz.in = 0.186,
                                   delta.hinf.in = 0.003,
                                   c.h.in = 0.005,
                                   gam.dis.in = 0.3,
                                   run_equilibrium = FALSE,
                                   equilibrium = output_equilibrium[[4]],
                                   print_progress = TRUE)
```
Variable coverage is specified with the ```treat.prob.variable``` input, and note that the ```treat.prob``` input is no longer specified, which previously gave a single coverage for all rounds.

If in the above model run ```print_progress = FALSE``` is called, but ```gv.trt = 1``` is also specified, only the duration of MDA will be printed (no progress updates). Currently, with ```print_progress = TRUE```, when the model run reaches each year in the simulation, the year and % progress will be printed as before.
Note that ```timesteps``` is the total number of years for which the model is run. ```treat.start``` and ```treat.stop``` are the years within this duration at which MDA is given.

To visualise the infection dynamics through time during annual MDA, use:

```{r}
tme <- seq(0, 30*366-1)/366

plot(tme, output_treat_annual$mf_prev, type = 'l', xlab = 'time', ylab = 'microfilarial prevalence', ylim = c(0, 1))

abline(v = seq(1, 25), col = 'grey', lwd = 0.1)

plot(tme, output_treat_annual$mf_intens, type = 'l', xlab = 'time', ylab = 'mean microfilarial intensity')

abline(v = seq(1, 25), col = 'grey', lwd = 0.1)
```

### 3.2.2 Variable timing (or frequency) of MDA

Assuming you have run the model to the endemic equilibrium (as described in secton 3.1), temporal infection trends during MDA specified with varying frequency (or different lengths of gaps between rounds) can be specified for a 25 year MDA programme by:

```{r}
timesteps = 30
treat.strt = 1; treat.stp = 26 #if model run stops in year 30, the last round is at the beginning of year 25
gv.trt = 1
trt.int = 1

treat.timing.in <-  c(1, 2, 3, 3.5, 4, 4.5, 5, 5.5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21,
                      22, 23, 24, 25)

output_treat_variable <- ep.equi.sim(time.its = timesteps,
                                   ABR = ABR.in,
                                   N.in = 440,
                                   treat.timing = treat.timing.in,
                                   treat.prob = 0.8,
                                   give.treat = gv.trt,
                                   treat.start = treat.strt,
                                   treat.stop = treat.stp,
                                   pnc = 0.05,
                                   min.mont.age = 5,
                                   vector.control.strt = NA,
                                   delta.hz.in = 0.186,
                                   delta.hinf.in = 0.003,
                                   c.h.in = 0.005,
                                   gam.dis.in = 0.3,
                                   run_equilibrium = FALSE,
                                   equilibrium = output_equilibrium[[4]],
                                   print_progress = TRUE)
```

Variable treatment timing over the course of the MDA programme is specified with the ```treat.timing.in``` input. Note that the ```treat.int``` input is no longer specified, which gave a fixed interval previously across all rounds. 

```{r}
tme <- seq(0, 30*366-1)/366

plot(tme, output_treat_variable$mf_prev, type = 'l', xlab = 'time', ylab = 'microfilarial prevalence', ylim = c(0, 1))

abline(v = treat.timing.in, col = 'grey', lwd = 0.1)

plot(tme, output_treat_variable$mf_intens, type = 'l', xlab = 'time', ylab = 'mean microfilarial intensity')

abline(v = treat.timing.in, col = 'grey', lwd = 0.1)

```

## 3.3 Vector control

Vector control is modelled in EPIONCHO-IBM by a proportional reduction in the annual biting rate (ABR), for a set period of time, as follows: 

```{r}

timesteps = 30
treat.strt = 1; treat.stp = 26 #if model run stops in year 30, the last round is at the beginning of year 25
gv.trt = 0 # no treatment given
trt.int = 1

output_VC <- ep.equi.sim(time.its = timesteps,
                                   ABR = ABR.in,
                                   N.in = 440,
                                   treat.timing = NA, #
                                   treat.int = trt.int,
                                   treat.prob = 0.65,
                                   give.treat = gv.trt,
                                   treat.start = treat.strt,
                                   treat.stop = treat.stp,
                                   pnc = 0.05,
                                   min.mont.age = 5,
                                   vector.control.strt = 3,
                                   vector.control.duration = 14,
                                   vector.control.efficacy = 0.75,
                                   delta.hz.in = 0.186,
                                   delta.hinf.in = 0.003,
                                   c.h.in = 0.005,
                                   gam.dis.in = 0.3,
                                   run_equilibrium = FALSE,
                                   equilibrium = output_equilibrium[[4]],
                                   print_progress = TRUE)

```

The following inputs specify vector control parameters: ```vector.control.strt``` specifies when vector control begins (which year); ```vector.control.duration``` specifies for how long (in years); and ```vector.control.efficacy``` specifies the efficacy of vector control (the proportional reduction in ABR), currently set to a default of 0.75.

We can visualise the impact of vector control with the following:

```{r}
# first we look at when the reduction in ABR occurs:

tme <- seq(0, 30*366-2)/366

plot(tme, output_VC$ABR_recorded, type = 'l', xlab = 'time', ylab = 'ABR', ylim = c(0, 1100))

# now we look at the impact on mf prevalence and intensity: 

tme2 <- seq(0, 30*366-1)/366

plot(tme2, output_VC$mf_prev, type = 'l', xlab = 'time', ylab = 'microfilarial prevalence', ylim = c(0, 1))

abline(v = c(3, 17), col = 'grey', lwd = 0.1) # lines specifying where VC period
mtext("Vector control period", side=3, line=0.5, at=9.5, col="darkgrey") # Rotated y axis label

plot(tme2, output_VC$mf_intens, type = 'l', xlab = 'time', ylab = 'mean microfilarial intensity')

abline(v = c(3, 17), col = 'grey', lwd = 0.1) # lines specifying where VC period
mtext("Vector control period", side=3, line=0.5, at=9.5, col="darkgrey") # Rotated y axis label


```

Future work will involve modelling vector control in a more sophisticated manner and to capture secular trends in biting rates. 



### 4. References

1. R Core Team. R: A language and environment for statistical computing. (R Foundation for Statistical Computing, 2018).

2. Csárdi, G. RCurl: Package ‘remotes’: R Package Installation from Remote Repositories, Including 'GitHub'. (2022). https://cran.r-project.org/web/packages/remotes/ 


